ABC inferences

### 2024-12-12 extensive_tests/draft-abc-inferences-vignette.Rmd
Updating last changes
Adding files and updates on draft abc inferences

---
title: "ABC inferences"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Introduction to MethEvolSIM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

- R packages: optparse (add to dependencies), parallel

@@

@@

>>>>

---
title: "ABC inferences"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{ABC Inferences with MethEvolSIM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

- R packages: optparse (add to dependencies), parallel, ape

@@

- An .RData file with a tree in ape format (TODO: modify this and check whether scrm is also producing trees in the same format)

@@

## Selection of the genomic region

1. [Download](https://www.ncbi.nlm.nih.gov/datasets/genome/GCF_000238955.4/) the *M. zebra* reference genome (GCF_000238955.4_M_zebra_UMD2a_genomic.fa) from the NCBI Assembly database. This genome is part of the M. zebra UMD2a assembly, which includes associated data such as gene annotations and other resources.

2. Transform CGI annotation (add citation) in txt format to BED

```{bash, eval = FALSE}
awk 'NR > 1 {print $1 "\t" $2-1 "\t" $3}' CGI-Mzebra.txt > CGI-Mzebra.bed
```
